---
title: "readme"
author: Basil Eric Rabi
date: September 15, 2017
output:
  md_document:
    variant: markdown_github
---

# mansched
R package with tools for manhours budgeting in Taganito Mine

## Installation

### R
This packages requires an [R](https://www.r-project.org/) version of at least
3.4.0 although it is recommended to install the latest version.

### java
Installation of mansched requires java
([jre](https://java.com/inc/BrowserRedirect1.jsp?locale=en)) to be installed 
first. 64-bit installation of R requires 64-bit installation of java while
32-bit installation of R requires 32-bit installation of java.

Install the appropriate version of java.

### devtools
mansched is only available via github.
To facilitate the installation of mansched, install
[devtools](https://github.com/hadley/devtools) first.

In R console, run:
```{r, eval=FALSE}
install.packages("devtools")
```

### mansched install
Once devtools is installed, run the following in R console:
```{r, eval=FALSE}
devtools::install_github('basilrabi/mansched')
```

## To do
* Introduce computation of employees under agency
    + Employees under agency costs 15% higher than seasonal employees
    + Expenses incurred for employees under agency are charged to contract fees
      others

## To do (Enhancements)
* Improve assigning of operator-class employees
    + At present, two priority levels are implemented in assigning:
        1. Employees with pre-defined cost code
        1. Employees with no cost code
    + Implement sub-priority levels of the above based on the number of
      authorized equipment.
    + A personnel with only one authorized equipment shall be the highest
      priority while the perosnnel with more authorized equipment shall be the 
      lowest priority.
* Speed up code
    + Look into multithreading or migrate some code to other language
